### 2020-01-20 methods.tex
minor update

\paragraph{Organization of this paper}
\charles{This could be moved to the end of the into also}
We want to study the effectiveness of product norm metrics in predicting trends in the
generalization accuracy of real-word, production quality, pretrained Deep Neural Networks.
In Section \ref{sxn:cv}, we study three well known, and widely available DNN CV architectures:
the VGG, the ResNet, and the DenseNet series of models.  We lay out the
basic methodology we use to evaluate the different metrics against the reported test accuracies. 
We also introduce the notion of Correlation Flow, and use this to 
compare the three pretrained architectures in detail.  
Then, in Section  \ref{sxn:nlp}, we look at several variations of a popular NLP DNN architecture,
the OpenAI GPT and GPT2 models.  We discuss when and how the different metrics apply more generally,
and where they differ.  In particular, we show where the layer Spectral Norm
 $\Vert\mathbf{W}\Vert_{\infty}$ behaves unexpectedly, and, contrastly, how
the $\alpha$ parameter can give insight into how well trained a model is.
Finally, in Section \ref{sxn:all}, we examine over 100 pretraind DNN CV models, and show
how well each metric is correlated with the reported test accuracies across different models
in an architeture series, and that the Alpha-Norm metric performs better.
----

>>>>

\paragraph{Organization of this paper}
\charles{This could be moved to the end of the into also}
We want to study the effectiveness of product norm metrics in predicting trends in the
generalization accuracy of real-word, production quality, pretrained Deep Neural Networks.
In Section \ref{sxn:cv}, we study three well known, and widely available DNN CV architectures:
the VGG, the ResNet, and the DenseNet series of models.  We lay out the
basic methodology we use to evaluate the different metrics against the reported test accuracies. 
We also introduce the notion of Correlation Flow, and use this to 
compare the three pretrained architectures in detail.  
Then, in Section  \ref{sxn:nlp}, we look at several variations of a popular NLP DNN architecture,
the OpenAI GPT and GPT2 models.  We discuss when and how the different metrics apply more generally,
and where they differ.  In particular, we show where the layer Spectral Norm
 $\Vert\mathbf{W}\Vert_{\infty}$ behaves unexpectedly, and, contrastly, how
the $\alpha$ parameter can give insight into how well trained a model is.
Finally, in Section \ref{sxn:all}, we examine over 100 pretraind DNN CV models, and show
how well each metric is correlated with the reported test accuracies across different models
in an architeture series, and argue the Alpha-Norm metric(s) perform remarkably well.
----
